\clearpage
\resheading{Projects}
\begin{itemize}

\item
	\ressubheading
		{CAVE In A Box, Master's Thesis}
		{}
		{Emerging Analytics Center, UA Little Rock}
		{Feburary 2016 - Present}
	\begin{itemize}
		\resitem{
			Designed a CAVE that is focused on mobility and low barrier 
			of entry
		}			
		\resitem{
			Designed supplemental software in Unity3D and Python to allow 
			other developers to build applications for this CAVE
		}
		\resitem{
			Used Autodesk Inventor to design the structure and then built 
			it by hand in the local workshop.
		}
		\resitem{
			Presented at the 2016 Arkansas EPSCoR/IDeA Foundation Conference
		}
	\end{itemize}

\item
   	\ressubheading
   		{GPU Raytracer For Learning}
   		{}
        {Intel Corporation}
     	{Summer 2019}
   	\begin{itemize}
       		\resitem{
       			Wanted to write an example in C for Metal to produce computer generated graphics.
       		}	
       		\resitem{
       			Followed Peter Shirley's Raytracing in One Weekend  
       		}
       		\resitem{
       			Resulting raytracer could render spheres with shadows. This limited feature set was intentional to show the minimum amount of work required.
       		}
        	\resitem{
                Most interesting part was the development of the random number generation as the language did not provide primitives to do so.
          	}
   	\end{itemize}

\item
   	\ressubheading
   		{GPU Radix Sort for Intel Processors}
   		{}
        {Intel Corporation}
     	{Summer 2018}
   	\begin{itemize}
       		\resitem{
       			C for Metal is the GPU programming language optimized for Intel GPUs 
       		}	
       		\resitem{
       			Previously, a hybrid approach was implemented to use both CPU and GPU. However, the paper “Revisiting Sorting GPGPU Stream Architectures” suggested that a pure GPU solution was better than hybrid approach due to the need for syncing and data transfers.  
       		}
       		\resitem{
       			Implemented the approached laid out by this research paper and benchmarked against the previous implementation.
       		}
        	\resitem{
       		   Found that there was a 26\% increase in performance and it could handle larger datasets efficiently.  
          	}
   	\end{itemize}

\item
	\ressubheading
		{Location-based Visualization on the Web}
		{}
        {Emerging Analytics Center, UA Little Rock}
   		{January 2018 - present}
	\begin{itemize}
   		\resitem{
            A client has a large dataset of locations and wanted the ability to visualize
            and discuss the data with colleagues.
   		}	
   		\resitem{
   			Using React, Redux, WebGL, Leaflet, and ArcGIS
   		}
   		\resitem{
   			Provide a number of new visualizations for the data such as area selection, tagging and filtering.
   		}
	\end{itemize}

\item
	\ressubheading
		{SPARTAN: An automatic tool to help determine patching}
		{}
        {Emerging Analytics Center, UA Little Rock}
   		{January 2016 - 2017}
	\begin{itemize}
    
    		\resitem{
    			Due to the security and reliability requirements and the sheer number / range of devices, patching is difficult.
    		}	
    		\resitem{
    			Helped create an initial desktop application to manage and visualize the data that was provided from companies
    		}
    		\resitem{
    			Ported desktop application to web interface after reviewing the client's need, further increasing the usability of the tool
    		}
       		\resitem{
       		   Conducted tests with live data at AECC facility in order to squash bugs and verify
               use cases.  
       		}
	
	\end{itemize}
    
\clearpage

\item
	\ressubheading
		{Porting Landmark Visualization to AR/VR }
		{}
		{Landmark Halliburton}
   		{Summer 2017}
	\begin{itemize}
    	\resitem{
   			Landmark Halliburton had engineering models in a traditional desktop
            application utilizing OpenGL and wanted to explore using both AR and VR
   		}			
   		\resitem{
   			Provided functionality to stream data from desktop application to 
            AR/VR space with Unity.
   		}
   		\resitem{
   			Developed a shared space where the AR/VR users are colocated by using 
            Proton Networking library.
   		}
	\end{itemize}


\item
	\ressubheading
		{Haptic Force Feedback}
		{}
		{Emerging Analytics Center, UA Little Rock}
		{April 2015 - August 2015}
	\begin{itemize}
		\resitem{
			Developed a physics simulation in OpenGL and C++ to test a 
			Haption 6DOF Robotic Arm.
		}
		\resitem{
			Designed a library and supplemental training materials to 
			make it easier for other developers to learn.
		}
	\end{itemize}

\item
	\ressubheading
		{Virtual Reality Touch Table}
		{}
		{Emerging Analytics Center, UA Little Rock}
		{May 2015 - October 2015}
	\begin{itemize}
		\resitem{
			Designed a structure to hold 2 consumer LCD touch screens 
			to create a Virtual Reality experience.
		}
		\resitem{
			Shown at the 2015 Supercomputing Conference in Austin, Texas
		}
	\end{itemize}


\item
	\ressubheading
		{Stair Climbing Robot, High School Thesis}
		{}
		{Arkansas School for Mathematics, Sciences and the Arts}
		{January 2013 - Feburary 2014}
	\begin{itemize}
		\resitem{
			Designed a Stair Climbing Robot to aid personnel as my 
			end of term project (thesis). Presented at the 2014 
			FIRM Competition. I recieved second place in the 
			Mechanical Engineering portion.
		}
		\resitem{
			Worked with Carl Frank and Nicholas Seward to design this 
			robot in Autodesk Inventor. Used a workshop to construct using 
			wood and 3D printing. Used a Raspberry Pi and Arduino to 
			drive the robot. The Raspberry Pi handled communication and 
			preiphials. The Arduino handled the drivetrain and recieved 
			commands from the Raspberry Pi.
		}
	\end{itemize}
	
\item
	\ressubheading
		{Sign Construction, Eagle Scout Project}
		{}
		{}
		{March 2014 - June 2014}
	\begin{itemize}
		\resitem{
			Volunteer work for the local Veteran's Memorial Hall exceeding 
			100 man hours.
		}
		\resitem{
			Designed a sign for their newly constructed building using 
			Autodesk Inventor
		}
		\resitem{
			Held design meetings with beneficiarys to confirm designs and 
			prototypes
		}
		\resitem{
			Orchestrated volunteers and materials remotely in order to 
			complete project.
		}
	\end{itemize}	
\end{itemize}
